Data Visualisation in R

### 2023-11-01 inst/tutorials/MSc_Data_Vis/MSc_Data_Vis.Rmd
Dealt with spacing issue with exercises

```{r Ex3test, exercise = T}

library(palmerpenguins)

@@

```{r Ex6, exercise = T}

@@

```{r Ex13, exercise = T}

ggplot(penguins, aes(x = bill_length_mm, y = bill_depth_mm)) +
  geom_point()

@@

```{r Ex14, exercise = T}

ggplot(penguins, aes(x = bill_length_mm, y = bill_depth_mm)) +
  geom_point() +
  stat_smooth()

@@

```{r Ex15, exercise = T}

ggplot(penguins, aes(x = bill_length_mm, y = bill_depth_mm)) +
  geom_point() +
  stat_smooth(method = "lm")

@@

```{r Ex16, exercise = T}

ggplot(penguins, aes(x = bill_length_mm, y = bill_depth_mm, colour = species)) +
  geom_point() +
  stat_smooth(method = "lm")

@@

```{r Ex17, exercise = T}

ggplot(penguins, aes(x = bill_length_mm, y = bill_depth_mm, colour = species)) +
  geom_point() +
  scale_colour_manual(values = c("blue", "red", "purple"))

@@

```{r Ex18, exercise = T}

ggplot(penguins, aes(x = bill_length_mm, y = bill_depth_mm, colour = species)) +
  geom_point(alpha = 0.8)

@@

```{r Ex19, exercise = T}

ggplot(penguins, aes(x = bill_length_mm, y = bill_depth_mm, colour = species)) +
  geom_point(alpha = 0.8, size = 3)

@@

```{r Ex20, exercise = T}

@@

```{r Ex21, exercise = T}

ggplot(penguins) +
  geom_point(aes(x = bill_length_mm, y = flipper_length_mm, colour = species))

@@

```{r Ex22, exercise = T}

@@

```{r Ex23, exercise = T}

ggplot(penguins, aes(x = species, y = flipper_length_mm)) +
  geom_violin()

@@

```{r Ex24, exercise = T}

ggplot(penguins, aes(x = species, y = flipper_length_mm)) +
  geom_violin() +
  geom_boxplot(notch = T)

@@

```{r Ex25, exercise = T}

ggplot(penguins, aes(x = species, y = flipper_length_mm)) +
  geom_violin() +
  geom_boxplot(width = 0.4, notch = T)

@@

```{r Ex26, exercise = T}

ggplot(penguins, aes(x = species, y = flipper_length_mm, fill = species)) +
  geom_violin() +
  geom_boxplot(width = 0.4)

@@

```{r Ex27, exercise = T}

ggplot(penguins, aes(x = species, y = flipper_length_mm)) +
  geom_violin(aes(fill = species)) +
  geom_boxplot(width = 0.4, fill = "grey90", notch = T)

@@

```{r Ex28, exercise = T}

ggplot(penguins, aes(x = species, y = flipper_length_mm)) +
  geom_jitter()

@@

```{r Ex29, exercise = T}

ggplot(penguins, aes(x = species, y = flipper_length_mm, colour = species)) +
  geom_boxplot() + 
  geom_jitter(width = 0.3)

@@

```{r Ex30, exercise = T}

ggplot(penguins, aes(x = species, y = flipper_length_mm, colour = species)) +
  geom_boxplot() + 
  geom_jitter(width = 0.3, alpha = 0.3) +
  theme_bw()

>>>>

```{r Ex3test, exercise = T}
library(palmerpenguins)

@@

@@

```{r Ex13, exercise = T}
ggplot(penguins, aes(x = bill_length_mm, y = bill_depth_mm)) +
  geom_point()

@@

```{r Ex14, exercise = T}
ggplot(penguins, aes(x = bill_length_mm, y = bill_depth_mm)) +
  geom_point() +
  stat_smooth()

@@

```{r Ex15, exercise = T}
ggplot(penguins, aes(x = bill_length_mm, y = bill_depth_mm)) +
  geom_point() +
  stat_smooth(method = "lm")

@@

```{r Ex16, exercise = T}
ggplot(penguins, aes(x = bill_length_mm, y = bill_depth_mm, colour = species)) +
  geom_point() +
  stat_smooth(method = "lm")

@@

```{r Ex17, exercise = T}
ggplot(penguins, aes(x = bill_length_mm, y = bill_depth_mm, colour = species)) +
  geom_point() +
  scale_colour_manual(values = c("blue", "red", "purple"))

@@

```{r Ex18, exercise = T}
ggplot(penguins, aes(x = bill_length_mm, y = bill_depth_mm, colour = species)) +
  geom_point(alpha = 0.8)

@@

```{r Ex19, exercise = T}
ggplot(penguins, aes(x = bill_length_mm, y = bill_depth_mm, colour = species)) +
  geom_point(alpha = 0.8, size = 3)

@@

```{r Ex20, exercise = T}
ggplot(penguins, aes(x = bill_length_mm, y = bill_depth_mm, colour = species)) +
  geom_point() +
  scale_x_continuous(breaks = seq(35, 60, 5))

@@

```{r Ex21, exercise = T}
ggplot(penguins) +
  geom_point(aes(x = bill_length_mm, y = flipper_length_mm, colour = species))

@@

```{r Ex22, exercise = T}
ggplot(penguins, aes(x = flipper_length_mm, fill = species)) +
  geom_density(alpha = 0.5)

@@

```{r Ex23, exercise = T}
ggplot(penguins, aes(x = species, y = flipper_length_mm)) +
  geom_violin()

@@

```{r Ex24, exercise = T}
ggplot(penguins, aes(x = species, y = flipper_length_mm)) +
  geom_violin() +
  geom_boxplot(notch = T)

@@

```{r Ex25, exercise = T}
ggplot(penguins, aes(x = species, y = flipper_length_mm)) +
  geom_violin() +
  geom_boxplot(width = 0.4, notch = T)

@@

```{r Ex26, exercise = T}
ggplot(penguins, aes(x = species, y = flipper_length_mm, fill = species)) +
  geom_violin() +
  geom_boxplot(width = 0.4)

@@

```{r Ex27, exercise = T}
ggplot(penguins, aes(x = species, y = flipper_length_mm)) +
  geom_violin(aes(fill = species)) +
  geom_boxplot(width = 0.4, fill = "grey90", notch = T)

@@

```{r Ex28, exercise = T}
ggplot(penguins, aes(x = species, y = flipper_length_mm)) +
  geom_jitter()

@@

```{r Ex29, exercise = T}
ggplot(penguins, aes(x = species, y = flipper_length_mm, colour = species)) +
  geom_boxplot() + 
  geom_jitter(width = 0.3)

@@

```{r Ex30, exercise = T}
ggplot(penguins, aes(x = species, y = flipper_length_mm, colour = species)) +
  geom_boxplot() + 
  geom_jitter(width = 0.3, alpha = 0.3) +
  theme_bw()
